SunPy - Python for Solar Physics

### 2014-01-08 Sunpy_paper_0.4.tex
Rename tex source
Add draft TOC and bib

\title{SunPy - Python for Solar Physicists}

\author{SunPy Developers}

\address{The Internet}
\ead{sunpy@googlegroups.com}
\begin{abstract}

SunPy contains too much awesome.

@@

\section*{References}
\begin{thebibliography}{10}
\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{thebibliography}

>>>>

\title{SunPy - Python for Solar Physics}

\author{S J Mumford}
\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of Mathematics and Statistics, The University of Sheffield, Hicks Building, Hounsfield Road, Sheffield, S3 7RH U.K.}

\author{J Bloggs}
\address{Wibble wiblle wiblle}

\ead{sunpy@googlegroups.com}

\begin{abstract}
This paper presents version 0.4 of SunPy a community developed Python package.
SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.

@@

\section{Core Data Types}

	\subsection{Map}

	\subsection{Lightcurve}

	\subsection{Spectra}

\section{Solar Data Retrieval}

	\subsection{VSO}

	\subsection{HEK}

	\subsection{HELIO}

\section{Visualisation}

\section{Coordinates}

\section{Development and Community}

\section{Future of SunPy}

%%% References
\bibliography{sunpy_paper_0.4}{}
